What's in a name? On the (automated) topic naming of software maintenance activities

### 2010-02-09 icpc/icpc2010.tex
updated refs and related work with Mockus 2000

>>>>

Mockus and Votta studied a large-scale industrial change-tracking system in ~\cite{Mockus00}. They also leveraged Wordnet, but only for word roots. They felt the synonyms would be non-specific and cause errors. A nice contribution was access to system developers, with whom they could validate their labels. Since we try to bridge different organizations, these interviews are infeasible (particularly in the distributed world of open-source software).
